Differences in care for patients experiencing left vs. right hemisphere ICH

### 2024-02-14 reports/aggressiveness.qmd
things work?

# load all targets objects
# tar_load_everything()
tar_load(non_surgery_trials)
tar_load(table_1_non_surgery)
tar_load(table_2_non_surgery)
tar_load(aggressive_dag)

@@

glimpse(non_surgery_trials)
skim(non_surgery_trials)

@@

table_1_non_surgery

@@

table_2_non_surgery

@@

aggressive_dag |>
  tidy_dagitty() |>
  node_status() |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(aes(color = status)) +
  geom_dag_edges() +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 51,
    color = "white", fontface = "bold", size = 4.5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20")

>>>>

# load all targets objects
# tar_load_everything()
tar_load(ich_aggressive)
tar_load(table_1_aggressive)
tar_load(table_2_aggressive)
tar_load(dag_aggressive)

@@

glimpse(ich_aggressive)
skim(ich_aggressive)

@@

table_1_aggressive

@@

table_2_aggressive

@@

dag_aggressive |>
  tidy_dagitty() |>
  node_status() |>
  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(aes(color = status)) +
  geom_dag_edges() +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 51,
    color = "white", fontface = "bold", size = 4.5
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20")
